Image Processing and geometrical analysis for edge detection during Gaz Tugnsten Metal Arc Welding

### 2011-06-21 articles/TIG/paper_bain3.tex

A numerical grey image can be described as 3D surface divided by a grid mesh
 in the X,Y plane. Each square represents a pixel and the relief surface at Z axis,
 the grey level. 
A strong relief change or high gradient greyness values at
 the image are perceived by human eyes as light changes, and can be interpreted
 as objects edges.

Sometimes, a regular relief patrons or regular greyness
 variation can be distinguished. The human eyes can perceive these patrons as texture 
and interpret the space between different textures zones as edges.
There exist a large spectrum of algorithms to image treatment, in particular for edges detection.
 Most of them can be classified by the way  is operated above the image pixels and grey level.

@@

The filters are algorithms that operate as mathematical functions $f$ above the 
$X$, $Y$ or both axis of the image ($Z = f(X,Y)$,  
$f(X)$ or $f(Y)$)  modifying his greyness value or $Z$ component. 
Different kind of filters can be mentioned as median, Gaussian, impulse,
 adaptive and others. The impulse filters such Canny are 
widely use to edge detection \cite{COCQUEREZ}. These filters have an
 impulse response to most important greyness gradient in the 
image; this allows the filter a better edges localisation
 (see figure \ref{fig::photo-explication-filter}). 
For this reason, Canny filter is widely 
used in the library to detect the welding elements edges. 
However, it is sensible to noise or secondary greyness gradients in the image
 and, in consequence, it have some difficulties to define closed surface.

@@

\subsection{ Image Features}
\label{image_features}

Before to propose an effective procedure using filtering or segmentation algorithms from erCv library, some image features imposed by the image acquisition procedure as: image view angle and image color, must be analyzed and modified.

\subsubsection{ Image Calibration}
\label{ image_calibration}

@@

\subsubsection{Image color}
\label{image-color}

As has been mentioned in section \ref{filters}, most of the filter type algorithm (including canny filter) operates as function over the image grayness levels. Moreover, the segmentation processing requires less computing time over 1-channels image than over 3-channels image. In order to allow to use filters algorithm and to do more efficient the image processing a function has been include into the treatment module to convert the color weld pool image to gray level image (see image \ref{photo-weldpool-grayness}).

@@

The idea is to recognize the weld pool from the raw image and therefore calculate his 2D surface area. This requires the identification of a well define weld pool contour. Several approaches could be uses to obtain the weld pool contour such as edge detection techniques  ( impulse filters) \cite{WU2}, Hough transforms \cite{OLSON} or geometrical weld pool division \cite{KOVACEVIC}. Nevertheless the most common approach is the image segmentation \cite{WANG}.

Thanks to the optical method acquisition (specular reflection), the mirror like surface of the weld pool reflect a uniform dark surface to the camera while the solid metal surface reflect a diffuse lighting surface \cite{WU2}.

A natural way to segment the images, could be separate it between the roughness (non homogeneous lighting zone) and non roughness zone or dark zone as the weld pool area (see figures \ref{photo-macro-drop-original}).

However the low intensity contrast between the weld pool and the surrounding solid metal due to the radiation from the pool, as well as the impurities or oxides presents on the weld pool (see figure \ref{photo-macro-drop-original}), prevents to use a simply approach of existing techniques to isolate the weld pool. Perform 2D contour require an effective techniques combination, to correct the light reflection distortion into the weld pool, isolate the weld pool and extract his contour.
% ; using to this the basic image processing concepts previous mentioned (see section
% \ref{image-processing-background}).

\subsubsection{Impurities and reflex correction}
\label{impurities-and-reflex-correction}

To apply segmentation techniques able to isolate the weld pool from the image, the arc reflects and the impurities over the weld pool have to be reduced.

Note that the impurities and the high intensities reflection appear as white or high gray level blobs into the dark or homogeneous low gray level weld pool (see figure \ref{photo-grayness-level}. An algorithm able to detect the ÔÕwhiteÕÕ blobs into the weld pool and correct its has been developed and included into the image treatment module of erCv. The algorithm use the same principia used by the well known red eye detections and corrections algorithm \cite{GAUBATZ}.

The white blob correction algorithm uses three threshold values to fix the blob selection criteria: $g\_upper$ to define the minimal gray level of the ÔÕwhite blobÕÕ, $g\_lower$ to define the maximal gray level of the weld pool and $s\_max$ to define the blob maximum pixel sizes.

@@

 \begin{eqnarray*}
 ( x, y) \in B\ \mbox{if} \\
gray\_level( x, y) > g\_upper \\
\mbox{Then}\ B\ \mbox{is in the weld pool if} \\
gray\_level( x, y)\ \leq\ g\_lower\ \forall\ (x,y)\  \in\  \partial B \\ 
\mbox{and if}\ size(B)\ <\ s\_max
 \end{eqnarray*}

If $B$ is in the weld pool, the grayness level at each pixel $(x,y)$ inside $B$ is replaced by the grayness average value of the grayness level pixels of $\partial B$ (see equation \ref{equation-grayness-recouvrement}). Then the ÔÕwhiteÕÕ blob is replaced by a low average grayness level surface, similar to the rest of the weld pool grayness level.

\begin{equation}
gray\_level( x, y) = \frac{gray\_level( x, y_{\partial B}) + gray\_level( x_{\partial B}, y) }{ 2}
\label{equation-grayness-recouvrement}
\end{equation}

@@

\subsubsection{ Texture Analysis Principia}
\label{texture-analysis-principia}

Now, the weld pool appears as a more uniform dark surface, which contrast with the non uniform gray level values of the surrounding solid metal area.
This particularity in the grayness level distribution (roughness) at the image could be interpreted as different textures zones \cite{MATERKA}, in the same the way as the eyes recognize the texture in the object surface and$/$or images.

The texture analysis method to perform image segmentation is an image processing technique widely uses in biomedicine, satellite recognition, industrial quality control and others fields requiring image processing. There exist different approaches to texture analysis, each one using their own image analysis methods: Structural, statistical, model based and transform methods \cite{MATERKA}.
The structural method requires complex logical analysis, while the transform and model based methods require mathematical analysis that required deterministic properties in grayness levels distributions \cite{MATERKA}. The statistical methods respond intuitively to what human eyes recognize: Two surfaces with different grayness level distribution or roughness.

As has been mentioned in section \ref{segmentation}, image segmentation means split into two or more fields the image. One field, would be mark in one color and the rest of the image in other color \cite{COCQUEREZ}.

\subsubsection{ Applying texture analysis}
\label{appliying-texture-analysis}

%\begin{figure}[h!]
%\begin{center}    
%\subfigure[Macro drop raw image]{\label{fig::photo-macro-drop-patron}\includegraphics[width=3.5cm,height=3.5cm]{figure5a.png}}
%\subfigure[Macro drop grayness image]{\label{fig::photo-macro-drop-grey}\includegraphics[width=3.5cm,height=3.5cm]{figure5b.png}}\\
%\subfigure[First smooth filter]{\label{fig::photo-macro-drop-smoothblur}\includegraphics[width=3.5cm,height=3.5cm]{figure5c.png}}
%\subfigure[Adaptive threshold per regions]{\label{fig::photo-macro-drop-adaptivethreshold}\includegraphics[width=3.5cm,height=3.5cm]{figure5d.png}}\\
%\subfigure[Median filter]{\label{fig::photo-macro-drop-smoothmedian}\includegraphics[width=3.5cm,height=3.5cm]{figure5e.png}}
%\subfigure[Canny filter]{\label{fig::photo-macro-drop-canny}\includegraphics[width=3.5cm,height=3.5cm]{figure5f.png}}\\
%\end{center}
%\caption{{\small Image treatment step by step of PGMAW process}}
%\label{fig::photo-macro-drop}
%\end{figure}

@@

%\begin{figure}[h!]
%\begin{center}    
%\subfigure[t1 ]{\label{fig::photo-results-macro-drop-t1}\includegraphics[width=3.5cm,height=3.5cm]{figure6a.png}}
%\subfigure[t2 ]{\label{fig::photo-results-macro-drop-t2}\includegraphics[width=3.5cm,height=3.5cm]{figure6b.png}}\\
%\subfigure[t3 ]{\label{fig::photo-results-macro-drop-t3}\includegraphics[width=3.5cm,height=3.5cm]{figure6c.png}}
%\subfigure[t4 ]{\label{fig::photo-results-macro-drop-t4}\includegraphics[width=3.5cm,height=3.5cm]{figure6d.png}}\\
%\end{center}
%\caption{{\small Images series of macro drop profiles}}
%\label{fig::photo-results-macro-drop}
%\end{figure}
%
%               
%                                  
%\begin{figure}[h!]
%\begin{center}    
%\subfigure[t = ]{\label{fig::photo-droplet-canny}\includegraphics[width=3.5cm,height=3.5cm]{figure7a.png}}
%\subfigure[t = ]{\label{fig::photo-droplet-alpha-shape}\includegraphics[width=3.5cm,height=3.5cm]{figure7b.png}}\\
%\end{center}
%\caption{{\small Images series of macro drop profiles}}
%\label{fig::photo-results-droplet}
%\end{figure}

A graph algorithm connects this segment and finds the longest closer segment.
 The longest closer segment corresponds to the metal transfer drop profile 
(see figure \ref{fig::photo-results-droplet}).

%\begin{figure}[h!]
%\begin{center}    
%\subfigure[t1 ]{\label{fig::photo-results-droplet-t1}\includegraphics[width=3.5cm,height=3.5cm]{figure8a.png}}
%\subfigure[t2 ]{\label{fig::photo-results-droplet-t2}\includegraphics[width=3.5cm,height=3.5cm]{figure8b.png}}\\
%\subfigure[t3 ]{\label{fig::photo-results-droplet-t3}\includegraphics[width=3.5cm,height=3.5cm]{figure8c.png}}
%\subfigure[t4 ]{\label{fig::photo-results-droplet-t4}\includegraphics[width=3.5cm,height=3.5cm]{figure8d.png}}\\
%\end{center}
%\caption{{\small Images series of macro drop profiles}}
%\label{fig::photo-results-droplet}
%\end{figure}

>>>>

A numerical grey image can be described as 3D surface divided by a grid mesh
 in the X,Y plane. Each square represents a pixel and the relief surface at Z axis,
 the grey level. 
A strong relief change or high gradient grey values at
 the image are perceived by human eyes as light changes, and can be interpreted
 as objects edges.

Sometimes, a regular relief patrons or regular greyness level
 variation can be distinguished. The human eyes can perceive these patrons as texture 
and interpret the space between different textures zones as edges.
There exist a large spectrum of algorithms to image treatment, in particular for edges detection.
 Most of them can be classified by the way  is operated above the image pixels and grayness level.

@@

The filters are algorithms that operate as mathematical functions $f$ above the 
$X$, $Y$ or both axis of the image ($Z = f(X,Y)$,  
$f(X)$ or $f(Y)$)  modifying his greyness value or $Z$ component. 
Different kind of filters can be mentioned as median, Gaussian, impulse,
 adaptive and others. The impulse filters such Canny are 
widely use to edge detection \cite{COCQUEREZ}. These filters have an
 impulse response to most important grayness level gradient in the 
image; this allows the filter a better edges localization
 (see figure \ref{fig::photo-explication-filter}). 
For this reason, Canny filter is widely 
used in the library to detect the welding elements edges. 
However, it is sensible to noise or secondary grayness gradients in the image
 and, in consequence, it have some difficulties to define closed surface.

@@

\subsection{ Image Adjustments}
\label{image_features}

Before to propose an effective procedure using filtering or segmentation algorithms from erCv library, some image physical characteristics imposed by the image acquisition procedure as: image view angle and image color, has been analyzed and modified.

@@

Concerning the image color, it has been mentioned in section \ref{filters}, that most of the filter type algorithm (including canny filter) operates as function over the image grayness levels. Moreover, the segmentation processing requires less computing time over 1-channels image than over 3-channels image. In order to allow to use filters algorithm and to do more efficient the image processing, a function has been include into the treatment module to convert the color weld pool image to gray level image (see image \ref{photo-weldpool-grayness}).

@@

The idea is to recognize the weld pool into the raw image, extract a well define weld pool contour and therefore calculate his 2D surface area. Several approaches have been developed and can be used to obtain the weld pool contour. The edge detection techniques \cite{WU2} as level set or impulse filters, the Hough transforms \cite{OLSON} or the geometrical weld pool division \cite{KOVACEVIC}; nevertheless the most common approach is the image segmentation \cite{WANG}.

Previous works \cite{WU2}, \cite{KOVACEVIC} have been showed that thanks to the optical acquisition method (specular reflection), the mirror like surface of the weld pool reflect a smoothness dark surface to the camera while the solid metal surface reflect a irregular grayness level surface. In the same the way as the eyes recognize the texture in a object surface and$/$or image, this particularity in the image grayness level distribution could be interpreted as roughness variations or different textures zones \cite{MATERKA}. And this propriety can be used to perform images segmentation dividing the image between the roughness zone and the smoothness dark zone (as the weld pool area, see figures \ref{photo-macro-drop-original}).

This technique know as texture analysis is an image processing technique widely used in biomedicine, satellite recognition, quality control and others fields requiring image processing. There exist different approaches to texture analysis, each one using their own image analysis methods: Structural, statistical, model based and transform methods \ref{MATERKA}. The structural method requires complex logical analysis, while the transform and model based methods require the identification and analysis of deterministic properties in the grayness level distributions \ref{MATERKA}. Finally the statistical method compares intuitively to what human eyes recognize: surfaces with an irregular grayness level distribution or roughness, which matches to what have been observed in the recorded images (see images \ref{}).

However the low intensity contrast between the weld pool and the surrounding solid metal due to the radiation from the pool, as well as the impurities or oxides present in both surface: (see figure \ref{photo-macro-drop-original}), induce error in the texture analysis. The impurities outside the weld pool, could be interpreted as dark smoothness zone like the weld pool and not as roughness zone, while the edge of impurities and light reflections into the weld pool could be interpreted as roughness zone. Therefore isolate the weld pool require more than a simply approach using one of the existing techniques. Indeed perform 2D contour require an effective techniques combination to correct the light reflection distortions and impurities, isolate the weld pool from the image and extract his contour.

\subsubsection{Impurities and light reflects correction on the weld pool}
\label{impurities-and-reflex-correction}

%Before isolate the weld pool from the image, the arc reflects and the impurities over the 
%weld pool have to be reduced.

Note that the impurities and the high intensities reflection appear as white blobs (high gray values set of pixels) into the dark weld pool (low gray values set of pixel, see figure \ref{photo-grayness-level}). An algorithm able to detect the ÔÕwhiteÕÕ blobs into the weld pool and correct its has been developed and included into the image treatment module of erCv. The algorithm use the same principia used by the red eye detections and corrections algorithm \cite{GAUBATZ}.

The white blob correction algorithm uses three threshold values to fix the blob selection criteria: $g_upper$ to define the minimal gray level of the ÔÕwhite blobÕÕ, $g_lower$ to define the maximal gray level of the weld pool and $s_max$ to define the blob maximum pixel sizes.

@@

\begin{eqnarray*}
( x, y)\ \in\ B\ \mbox{if} \\
gray\_ level( x, y) > g\_ upper \\
\mbox{Then}\ B\ \mbox{is in the weld pool if} \\
gray\_ level( x, y)\ \leq\ g\_ lower\ \forall\ (x,y) \in\ \partial B \\ 
\mbox{and if}\ size(B)\ <\ s\_ max
\end{eqnarray*}

If $B$ is into the weld pool, the gray value at each pixel $(x,y)$ inside $B$ is replaced by the gray average value of the gray value pixels of $\partial B$ (see equation \ref{equation-grayness-recouvrement}). Then the ÔÕwhiteÕÕ blob is replaced by a low average grayness level surface, similar to the rest of the weld pool grayness level.

\begin{equation}
gray\_level( x, y)\ =\ \frac{gray\_level( x, y_{\partial B}) + gray\_level( x_{\partial B}, y) }{ 2}
\label{equation-grayness-recouvrement}
\end{equation}

@@

\subsubsection{ Impurities and light reflects corrections surrounding the weld pool}
\label{impurities-and-light-reflects-corrections-surroinding-the-weld-pool}

As mentioned the presence of some oxides impurities into the solid metal surface, closer to the weld pool edge, rest a mayor problem to image segmentation. A combination of filtering and segmentation techniques has been applied to reduce the brightness points and dark zones due to impurities presence into the roughness zone.

First, an impulse response filter to grayness level gradient is applied (Canny filter). This edge detection filter converts the grayness level images into images composed only by white segments, which represent the edges profile. Adjusting the filter parameters to maximum gradient detection, the canny filter read the irregular grayness level distribution as multiple grayness level gradients. Then the roughness surfaces are converted into irregular white segments distributions and the smoothness zone are converted into zero level zones (black zones) with some white segments, as the weld pool. The impurities appear as small black zones surrounded by numerous white segments into the roughness zone or solid metal surface (see image \ref{}).

The idea is replace the roughness zone by a more homogeneous white surface recovering the small black zones. A dilate filter have been applied (twice) to enhance the white segments up to small white surfaces reducing the small black zones corresponding to the impurities into the solid metal surface. This filter operate taking the maximum value over a $3\times 3$ pixel neighborhood. A smooth classical filter (blur) have been used to smooth the ÔÕwhite surfaces edgeÕÕ. This filter replaces the values of squares of $5\times 5$ pixels by their average values. The small black zones into the biggest white surface appears diffused due to the smoothness effect over the edges (see figure \ref{}). The same effect is observed into the biggest black zone (weld pool), where the small white surfaces become highly diffused. Then, a median filter types have been used to enhance the image by gray values region, and homogenized the surfaces. This filter compute the grayness median value over $5\times 5$ pixels region. The image is enhance in his black (weld pool) and white (solid metal) regions (see image \ref{}), resulting in more homogeneous white and black surfaces.

\subsubsection{Completing the image segmentation}
\label{completing-the-image-segmentation}

In order to recognize and isolate the weld pool element (central black surface into the image, see image \ref{}),  a segmentation statistical algorithm have been applied. A small region of interest (ROI) is defined into the weld pool. Then the algorithm scans the image surface by regions of equal ROI size. The algorithm find similarities to the ROI using a normalize correlation method.  The gray values of the resulting regions are adjusted depending their level of correlation with the ROI; $0$ gray value means non correlation at all while $255$ gray value means that it is the same surface. Note that the weld pool became the big central white region (see image \ref{})

A threshold of type binary have been applied to enhance the edge of the white surfaces, converting the image into a binary white and black regions follows the criteria:

$
\begin{array}{l}
gray\_ level\_ threshold(x,y) = 
\end{array}
\left\{ 
\begin{array}{lcr}
    0 & if & gray\_ level\_ original(x,y)\ <\ 200 \\
255 & if & gray\_ level\_ original(x,y)\ \geq\ 200 
\end{array}
\right\} $

Where $gray_level_original(x,y)$ is the gray value of a image pixel before threshold and $gray_level_threshold$ is the gray value assign to the pixel after threshold.

Finally a Canny filter has been applied to extract the principal edges presents in the image. Note that for a binary image all edges are principal, therefore Canny detect all edges presents into the image (see figure \ref{}).

@@

Despite the performance achieved by the image processing, the canny filter generates many edges or strings into the image. These strings are composed by white points and are interpreted by the algorithms as individualÕs points. In order to automate the weld pool edge extraction process, geometrical and graph algorithms have been used to connect the points belonging to the weld pool border, convert it into connected segments and compute the area surrounded by the segments.

Note that the weld pool appears as the biggest closer string into the image (see figure \ref{}). The idea is to build segments around the string and take the longest closer set of segments.

Give $S$ the set of points into the space image. The segments could be built between wherever two points of $S$. However to fulfill the strings with segments, only the points placed together could define a segment. To choose the correct point of $S$ a Delaunay Triangulation is made over $S$ \cite{CGAL}. Each point of $S$ is a vertex of a triangle and then each potential segment is an edge of a triangle. The Delaunay triangulations guarantees a unique solution with minimal internal angles for each triangle, which means minimal length sides to the triangles \cite{BERG}. Give $\beta$ the string surrounding the external hull of the Delaunay triangulation of $S$. An alpha shape algorithm uses a  $\alpha\ \in\ N$ parameter, or square radius of a test  circle, to travel from outside $\beta$ to inside the triangulation. The  circle has to go  through the triangles sides without  touching  the vertices. Give $n$ the number of triangles  sides of the triangulation and $l_{i}$ with $i\ \in\ {1,n}$ the length  of each side, if $\sqrt{\alpha}\ >\ l_{i}$ with $i\ \in\ {1,n}$ , a segment is marked between the respective vertices or points. At the end of the process, a set of segments knows as $\alpha$-shape has been created. Note if $\sqrt{\alpha} > l_{i}\ \forall\ i$, the circle can not go inside $\beta$, then $\alpha$-shape is $\beta$ \cite{CGAL}. If $\sqrt{\alpha}\ <\  l_{i}\ \forall\ i$ the circle go through every side in the triangulation, then  no segment  is created and $\alpha$-shape became $S$. The points that compound the weld pool borders are all contact neighbors. Then $\alpha\ =\ 1$ is sufficient to create a segment set around the droplet (see figure \ref{}).

A graph algorithm connects these segments and finds the longest closer segment. The longer closer segment corresponds to the weld pool perimeter (see figure \ref{}).
